%!TEX root = ../../../super_main.tex

\chapter*{Preface}
This report is created by project group SW808F16 from the Software Master's programme at Aalborg University as part of their second semester spanning from February 2016 to May 2016. The overall theme of the project is \emph{Mobile Systems}, spanning over topics such as smartphone applications, wearables, other ubiquitous, intelligent homes and more. This report is focused around how we can apply such technologies to allow companies, researchers and the like a more accessible way of performing reality mining. 
% The source code of the developed product can be found on the attached CD in \appref{app:cd}.
\\\\
This project work has been done in a \emph{Problem-based learning} setting, which is known as \emph{The AAU model} at Aalborg University. Therefore a semester is split into group-based project work and supporting courses. The members of the project group behind this report followed the same courses this semester. The courses were \emph{Advanced Programming}, \emph{Test and Verification}, and \emph{Software Innovation}. Methods and techniques learned during these courses have been applied throughout the project.
\\\\
We invite the reader to try out the developed project. Feel free to do whatever with the both the Android and web applications. Installing the Android application can be done by downloading the compiled \mono{.apk} file on the GitHub release page found at:

\begin{center}
	\mono{\href{https://github.com/Shaderex/SW8-Android/releases/tag/3.1/}{https://github.com/Shaderex/SW8-Android/releases/tag/3.1/}}	
\end{center}

The web application is available on one of the following websites. If you are on the AAU network, please use the \mono{local} version, otheruse use the \mono{global} version. Note, that the Android application and this website are \emph{linked}, meaning that changes, or additions, made on the website will be available in the Android application. If you do not wish to register a new account, the following credentials may be used.

\begin{center}
	\mono{\href{https://prod.local.element67.dk:8000/}{https://prod.local.element67.dk:8000/}}
	\mono{\href{https://prod.global.element67.dk:8000/}{https://prod.global.element67.dk:8000/}}
\end{center} 

\vspace{-2em}

\begin{align*} 
\text{\mono{Username}} &: \text{\mono{test-user@test-user.com}} \\ 
\text{\mono{Password}} &: \text{\mono{thisisasecret}}
\end{align*}

% Reading guide
\input{content/miscellaneous/preface/reading_guide.tex}

% Chapter overview
\input{content/miscellaneous/preface/chapter_overview.tex}

