%!TEX root = ../../super_main.tex
\section{Consumption of Battery and Disk}

As mentioned in SECTION\todo{ref to good engineering practices}, we do not want to reactivate a mobile data network modem, i.e. a cellular connection, regularly and we do not want the client application to be dependent on always having a reliable network connection. Instead of streaming the data gathered from the senors directly to the server we store it persistently on the device in order to send it in bulks whenever the modem is already active. By doing this we save a lot of battery time, in fact the larger bulks we send to the server at a time the more energy is saved. We also want to avoid using cellular communication when uploading the data for two reasons. One reason is that this type of communication, typically, is metered per byte sent from the participant. A second reason is that this type of communication, typically, is slower and for that reason requires the modem to be active for longer periods of time, hence consuming more battery. If we try to utilize the WiFi instead as much as possible and at the same time send the data in as big chunks as possible we save energy, however we do not want to occupy the disk capacity of the device entire if the campaign is intended to gather a lot of sensor data rapidly over a long period of time. For this reason we have designed some heuristics which tries to decrease the battery consumption while still trying not to overflow the device's disk with sensor data.

\todo{When we have designed this, write it here!}
