%!TEX root = ../../super_main.tex

\chapter{Development Method}
\label{cha:development_method}

This chapter gives an overview of the applied software methodologies that we followed during the project period. We chose to follow an agile development method called Extreme Programming (XP) \parencite{xp}, with a few changes, which is described in this chapter. The main reason why we considered XP, was because we wanted a more concrete approach, with engineering practices, and test-driven method compared to other agile methods such as Scrum, which we have had experience with on previous semesters. Besides using XP, we chose to also utilize the Essence methodology \parencite{essence_book} to some extent, which is an innovation driven methodology. This chapter contains some description of how we have followed XP and applied elements from Essence, and discusses how these will contribute to our project.

\section{Development Methodologies}
\label{sec:development_methodologies}
\todo[inline]{Overvej at vi har 0 kilder i det her afsnit}
There exist various methodologies in software development. The most common practice in traditional software development is the document driven waterfall approach. This approach emphasizes that the developers should put a lot of effort in planning and separating the development in parts. For instance a software project could be separated into five parts:
\\
\begin{itemize}[noitemsep]
    \item A part for analyzing and understanding the problem domain at hand, hence producing a requirement specification. 
    \item A part for designing the product, hence converting requirements into a design document, that describes which technologies should be utilized,  and architecture of the system. 
    \item A part for implementing the product based on the design.
    \item A part for testing if the system is stable, and verifying that the requirements are met. 
    \item A part that focuses on maintaining the developed system. 
\end{itemize}

A waterfall approach encourages specialization, under the assumption that having specialists for every separate part produces a better product. An example of such an assumption is that an experienced tester could develop better tests than an architect. This development methodology spends a lot of resources on producing documents, because the flow of work often shifts from one expert to the another, in order to share knowledge. 
\\\\
This paradigm does not handle change very well; it relies on a stable and well formulated requirement specification. The agile development paradigm builds on embracing change and caring less for contracts and other documents. Agile development instead encourages continuous interaction with the customer during the development of a system. By doing this, a development team has greater ability to adapt to changing requirements from the customer during the development of a system, and the team can spend more time on developing a viable system, rather than on specifying what the customer wants in as great detail as possible. Agile development furthermore discourages having experts, and encourages generalists instead.
\\\\
An issue with the agile methodology is that it, in many cases, is highly dependent on some sort of customers, and delivering a product. The Essence methodology tries to deal with some of these issues by adding to the existing methodologies and not replacing them. Essence is focused around innovation and steering a project in the direction that will create the most value. In this project we have chosen to utilize an agile development methodology, Extreme Programming (XP), as our primary development method, whilst trying utilize some of the creative tools and techniques that the Essence methodology suggests. 

\input{content/method/extreme_programming}
\input{content/method/essence}


