%!TEX root = ../../super_main.tex

\subsection{Server workload distribution}

A dimension which would have to be considered when batching of network tasks, as we do, is the distribution of workload on the server. Requiring that the phone is charging, which we do not require, would for instance likely distribute workload towards the nightly hours where people tend to charge their mobile devices while sleeping. This might prove to be a problem that would have to be taken into account when the system is introduced to a lot of participants.  

\subsection{Data Source Availability Requirements}

We have thought about allowing customers specify different levels of requirements for sensor and data source availability. It might be acceptable for some data sets to have missing values for some of the sensors while requiring that readings from other sensors must be present. This could for instance mean that some campaigns might require the presence of a certain sensor, say a heart rate sensor, while having for instance the Wifi data source optional and only included if available, i.e. turned on by the participant. The different levels requirements for sensor availability could both be in regards to the actual capability of devices involved by the participant, i.e. that the involved devices must support the desired readings, and in regards to the availability of the reading, i.e. in cases where the devices include the data source or sensor but it is for some reason temporarily unavailable. We have however not implemented this and data is simply not included in the snapshots if the sources where unavailable at the time.
