%!TEX root = ../../super_main.tex

\section{Ethical Considerations}
\label{sec:ethical_considerations}

With the increasing use of devices in a society where everything is being digitized, the gathering of data also increases. This digitization means that all sorts of data are being collected about the average citizen. This data collection happens in both the public sector and private sectors. The government, as part of the public sector, gathers information regarding health and taxing, while companies such as Facebook and Google gathers personal data regarding the users behavior using their applications. With the increasing amount of data being gathered, coming from personal devices such as smartphones and wearables, considerations about how one store this type data becomes increasingly important. Professor of IT-ethics at Aalborg University deemed that personal data is one of the largest ethical dilemmas in the recent and upcoming years.

\quotewithref{
    Med et voksende antal private og offentlige registre, hvortil flere og flere får adgang, vokser risikoen for tab af følsomme personoplysninger og misbrug af data. Det er det største etiske dilemma, vi går i møde i 2015.
}{etik_dk_thomas_ploug}\todo{Find a decent way to translate this quote (also the author of the source is not Thomas Ploug, but he is the one being quoted [\#AskHolm])}

Experts deem that abuse of these type of data are becoming an increasing risk, and for that reason when developing systems that gathers personal information, the way they are stored transfered, and in general used, must be taken into consideration. There exist legislation in Denmark that should ensure that these issues are being treated with care. However, because the value of personal data increases for malicious parties as well as non malicious parties, the devastation of it being accessible to the wrong people also increases. It should be in everyones interest to treat these personal data with care, since users have no direct control of how these data are access or who have access to it. Bill Schmarzo, chief technology officer for EMC Global Services, an influential cloud computing and -storage company, is particular concerned with unauthorized parties accessing personal data.

\quotewithref{
    But the bigger concerns are related to unsanctioned organizations using my data and inferences about my interests, passions, affiliations and associations for borderline uses about my political, religious, sexual, etc. preferences.
}{forbes_bill_schmarzo}\todo{Same issue that Bill Schmarzo is not author but the one being quoted}

A safe and secure infrastructure should be established in systems operating with information that have potential to harm the people it was gathered from.