%!TEX root = ../../super_main.tex
\section{Participant Experience Evaluation}
\label{sec:participant_experience_evaluation}

We want uMiner to be as general as possible in terms of who participants might be. Meaning that we want to target as many different personas as possible in terms of user experience of the Android application. We have for this reason tried to create some sort of user experience evaluations in regards to the part of the system the participants are going to use. The idea of this evaluation is to determine if there are some obvious flaws in the design of how our Android application in regards to disturbing the participants. We want to investigate if we developed a solid start for part of the client application that notifies and asks the participants questions. This evaluation was performed with five people having a compatible smartphone, firstly this is not a great deal of test subjects and does not provide any statistical evidence for the evaluation of the system, but we hope to get some constructive evaluation of the application never the less. Furthermore one should not that the persona of these five test subjects are rather similar. All five are male in their start 20s, with similar interests, all being tech savvy some extend.

\subsection{Setup}
\label{sub:setup}

We have created a test campaign called ``Alcohol and you'' which should emulate the type of campaign a final customer might specify. The campaign specification can be seen in \tabref{tab:test_campaign_spec}. This specification means that we take 600 measurements every hour and we desire answers for a questionnaire every other hour.

\begin{table}[!htbp]
    \centering
	\begin{tabular}{|m{0.3\textwidth}|m{0.7\textwidth}|} \hline
	Total duration        & 2 hr                                                                                                                                                                                                                                                           \\ \hline
	Sample frequency      & 1 min                                                                                                                                                                                                                                                          \\ \hline
	Sample duration       & 2 sec                                                                                                                                                                                                                                                          \\ \hline
	Measurement frequency & 200 mili sec                                                                                                                                                                                                                                                   \\ \hline
	Sensors               & \begin{itemize}[noitemsep]
								\item Accelerometer 
								\item Ambient Light
								\item Barometer
								\item Compass
								\item Gyroscope
								\item Location
								\item Proximity
								\item Galvanic Skin Response (Microsoft Band 2)
								\item Heartbeat (Microsoft Band 2)
							\end{itemize} \\\hline
	Questions             & \begin{itemize}[noitemsep]
								\item Have you within the last hour had an alcoholic beverage?
								\item Have you within the last hour had a carbonated alcoholic beverage?
								\item Have you within the last hour had a strong alcoholic beverage with (more than 10\% alcohol)?
								\item Do you feel influenced by alcohol?
							\end{itemize} \\ \hline
	\end{tabular}
	\caption{Alcohol and you specification}
	\label{tab:test_campaign_spec}
\end{table}
\FloatBarrier

The application was distributed and installed on devices of test subjects, and they were guided to how they could start contributing to our test campaign. This means that this test does not in any way evaluate the main activity of the system, it only evaluates the experience of being notified by the application and prompted with questions. After the setup of the application we told the test subjects to proceed with their daily life and treat the uMiner application as any other application the might have installed from the Google Play Store. 

\subsection{Results}
\label{sub:results}
After 24 hours of the application being installed on the test participants devices we asked them a series of questions to understand the disturbance of the notifications and questionnaire throughout one day of experience. The results of this survey can be seen in \tabref{tab:survey_result}

\todo[inline]{Prettify table and translate}
\begin{table}[]
\centering
\caption{Result of the survey.}
\label{tab:survey_result}
\begin{tabular}{|m{0.7\textwidth}|m{0.3\textwidth}|} \hline
Hvor god føler du dine evner er til at benytte en smartphone? (1-5)                                           & 3: 20\% , 4: 40\% , 5: 40\%			  \\ \hline
Har du følt dig generet af uMiner applikationen?                                                              & Ja: 20\% 							  \\ \hline
Hvor meget følt du den generede dig? (1-5)                                                                    & 2: 100\% 							  \\ \hline
Hvor ofte ignorerede du spørgsmålene (notifikationerne) du fik?                                               & Ingen: 80\% , \textgreater 50\%: 20\% \\ \hline
Har du på noget tidspunkt haft lyst til at afinstallere uMiner mens den har været installeret på din telefon? & Nej: 100\% \\ \hline
\end{tabular}
\end{table}


\todo[inline]{Mention the feedback regarding "Hvis jeg ikke var fuld 6.20 om morgenen er jeg det sku nok heller ikke klokken 8 og klokken 10"}
%Hvorfor ignorerede du spørgsmålene?
%Hvis jeg ikke var fuld 6.20 om morgenen er jeg det sku nok heller ikke klokken 8 og klokken 10