%!TEX root = ../../super_main.tex

\subsection{Data Quantity Estimation}
\label{sec:data_quantity_estimation}
%This gave us a dataset with a size of 142908 bytes. This experiment would then yield a data set of approximately 205 MB if it was run for a day. Running the same experiment for 30 days with 100 different devices would then approximately yield a data set of 617 GB assuming similar mobile devices with similar sensors. This quick napkin math was only for one sensor with 100 people and this could quickly escalate if more sensor or more people are added.

\todo[inline]{Overvej: Lav en reference til vores user story, og fortæl hvor meget data vi samler om dagen med disse målinger. Skriv også at dette KUN er RÅ sensor output, stored i Java-hukommelse størrelser. Med snapshot struktur er det meget værre} 

In order to comply with the problem statement in \secref{sub:problem_statement}, we want to minimize the effect that our application has on the daily mobile lives of the participants. One aspect that might affect this is the battery consumption and network usage of our application. We would therefore like to minimize these factors. In order to know if we at all should bother with this minimization, we have estimated the size of the data, if we were to use it as a raw stream. We have done this by experimenting with different continuous sensors on a Nexus 5 smartphone and logged all values captured from the sensor for 1, 5, and 20 minutes. The results of these tests can be seen in \tabref{tab:sensor_experiment}. Note that the compass sensor is a virtual sensor, which uses data collected from both the accelerometer and magnetometer, hence the correlation between the data sizes ($142 \text{KB} + 35 \text{KB} = 177 \text{KB}$ for 1 minute). These tests were only performed for four different sensors, but customers might need data from several different sensors, thus further increasing the amount of data collected. These quantities of data might present a problem even on modern mobile platforms due to paid limited data plans and battery consumption. There might be different data needs, some customers might require very detailed data from many sensors from a few devices and others might require more sparse data from a few sensors from a lot of different devices. However, we can conclude that gathering a continuous stream of data from all sensors all the time is not a viable solution in all cases.

\begin{table}[!htbp]
\centering
\begin{tabular}{l|c|c|c|c}
\textbf{Sensor}     & \textbf{Accelerometer} & \textbf{Gyroscope} & \textbf{Magnetometer} & \textbf{Compass} \\ \hline
\textbf{1 minute}   & 142 KB                  & 143 KB             & 35 KB                 & 177 KB               \\ \hline
\textbf{5 minutes}  & 714 KB                  & 714 KB             & 178 KB                & 892 KB               \\ \hline
\textbf{20 minutes} & 2,859 KB                & 2,859 KB           & 715 KB                & 3,573 KB                
\end{tabular}
\caption{Data size of sensor data collection after a set amount of time.}
\label{tab:sensor_experiment}
\end{table}
\FloatBarrier