%!TEX root = ../../super_main.tex

\section{Compression}
\label{sec:reflection_compression}

At some point in time after we created the compression method for three floats described in \secref{sec:compression}, we had to send the data to the server, and for this we decided to use the JSON format for transferring data. This resulted in the insertion of \mono{FloatTripleMeasurements} into the JSON which was sent as HTTP requests. When the server receives a snapshot, the entire JSON string is inserted into the PostgreSQL database as a \mono{text} type, which is a varying unlimited length string type. This means that, when we want to display the JSON to the customers, we would have to decompress our \mono{FloatTripleMeasurements}, somewhere in the middle of the JSON, before the data is useful for the customers.
\\\\
When we created the \mono{FloatTripleMeasurement}s on the Android side, we immediately made sure to create a decompression algorithm on our server in PHP, so we could handle it however we decided to. Sadly, we did not have the time to create the appropriate processing of snapshots on the server. This results in having to decompress the \mono{FloatTripleMeasurement}s on the Android side before sending the data, which defeats the primary purpose of the compression. Thereby we both spend power on compressing and decompressing the data on the phone,  which therefore negatively affects the participants. We could alternatively have created a much more detailed database schema, instead of storing the snapshots as JSON. This would have allowed us to store the float triples separately on the server and thereby allowed us direct access them directly when they needed to be decompressed.


