%!TEX root = ../../super_main.tex

% ==== METHOD REFLECTION ====
\section{Development Method}
The development method that we have employed throughout the project have in general worked well for us, but there are some aspects that we feel have been very time consuming. 
\\\\
Our experience shows that a user story and an acceptance test coexist in a mutual relationship. A user story draft is usually formulated first and a draft for an acceptance is then designed. The user story and acceptance test drafts are then revised back and forth until everyone claims to have understood both and have agreed on their semantics. This helped us get a mutual understanding of the task and also solve potential ambiguities. 
\\\\
Another aspect that helped us clarify the intention and solve ambiguities was the estimation of user stories. We discovered that planning poker, which we have used to estimate tasks in iteration planning, is more valuable to us than simply being a technique for estimating tasks. Many ambiguities in task cards were discovered automatically by estimating and having short discussions about a given task. We learned that time estimation discussions quickly transformed into discussions about the semantics of the tasks when there were significant disagreements. We embraced these discussions and found that they were great means to resolve ambiguities and knowledge sharing. Time estimation discussions, when performing planning poker, are in general time boxed, but we allowed longer discussions when we felt that task cards should be updated in order to resolve ambiguities or if we felt that tasks should otherwise be split or clarified.
\\\\
Even though the discussion during estimation made the tasks more clear, it made estimation a long task. Nearing the end of the project period (approximately the last two-three iterations) the time schedule was becoming increasingly tighter, and we therefore changed from estimating all created tasks to only estimating tasks until we had enough work hours to fulfill the iteration work schedule. By making this change, we felt that we were not wasting time, and we therefore embraced this shift in development methodology. Even though this change was made we still were not at a pace that would yield a product that we could be satisfied with. Therefore, the last iteration planning was made quite differently. Everyone contributed in the creation of the tasks and user stories, but when they were to be estimated, only two persons were involved, whilst the other members of the group worked on the report and product. Even though it might seem controversial to estimate the task in such a way, the estimated time was close to the actual spent time. The benefit was not only that other developers could focus on other tasks during the estimation, but the time spent on the estimation was low compared to the usual planning meetings. Even though we lost the group wide discussion there were no problems with ambiguities or tasks otherwise being unclear. This made it clear to us that a every development method has its pros and cons, and that the work flow in a team can be improved by adjusting the method and trying different things. 
\\\\
% Roles: customer, tester, developer, and participant
Another aspect that worked well for us during the planning meetings was the roles that we used. The different roles inspired different ways of thinking about the problem area from different points of view. Roles ensured this by making sure that at least one person had a given responsibility. The tester role, for instance, had to constantly be critical of whether the discussed features were actually testable or if they were too loosely defined. 
A potential pitfall that we discovered when using this form of role playing, was that people sometimes would be too bound their role, and potential creativity would be limited or other valuable inputs would be lost.
\\\\
The short iterations we used during the development have assisted with the steering of the project as was expected. It allowed us to have higher accuracy between iterations, which effectively meant that it was easier for us to focus on individual areas and gain insight in what areas needed attention, meaning that it also increased the knowledge sharing in the group. The  ceremonies that were supposed to increase the knowledge sharing in the group, namely stand up meetings and pair programming, also worked as expected. We have in earlier semesters experienced that the daily stand up meetings would, over time, stop being daily and later even skipped for very long periods of time. However, during this semester this has not been the case, which we believe can be contributed to the fact that we did not use a digital task board, but rather a physical one, which was used as a center point for the meetings. 
\\\\
As mentioned in \charef{cha:development_method} we have in our project work utilized the Essence methodology. This methodology has in general helped us consider the direction of our work, and inspired discussion and reflection of how we best would solve the problem at hand. An issue that we encountered in using the essence methodology was that it would take a lot of time away from actual development and documentation of our work. This might be due to the fact that we were introduced to it this semester, meaning that we had no prior experience or knowledge about it. The fact that the methodology was introduced in this semester additionally meant that as the semester progressed we would be introduced to more and more concepts that might have been beneficial to utilize in the beginning of a project. Some of these concepts included different artifacts that could have been a valuable addition to our work and report, however, at the time they were introduced it was to late to use them as intended.
\\\\
One of such items were the configuration table shown in \appref{app:configuration_table}. We only finished this configuration table late in the project. The intended use of the table is to create one, or rather evaluate and change an existing one, for each iteration, however, we only finished this table nearing one of the last iterations that we had. Otherwise the table was meant to keep an overview of the different aspects of the project, and should be a tool for continuously evaluating whether a project in all aspects were moving in the most optimal direction. This artifact was one of the items that we felt took a long time to create, but it still provided us with valuable insight in our project, and inspired a lot of discussion of how to best tackle problems. In general, many of the, for us, longsome tasks, might be quicker, if we were to use them again, due to the experience we have gained from working with them in this project. Furthermore, this table could be useful for future iterations, if anyone chooses to pursue the continued development of the project.

