%!TEX root = ../../super_main.tex

\chapter{Reflection}
\label{cha:reflection}

% ==== METHOD REFLECTION ====
\subsection{Extreme Programming Reflections}
We have discovered that planning poker, which we have used to estimate tasks in iteration planning, is more valuable to us than simply being a technique for tasks estimation. Many ambiguities in task cards were discovered automatically by estimating and having short discussions about a given task. We learned that time estimation discussions quickly transformed into discussions about the semantics of the tasks when there were significant disagreements. We embraced these discussions and found that they were great means to resolve ambiguities. Time estimation discussions, when performing planning poker, are in general timeboxed, but we allowed longer discussions when we felt that task cards should be updated in order to resolve ambiguities or if we felt that tasks should otherwise be split or clarified.
\\\\
The short iterations we used during the development have assisted with the steering of the project. It allowed us to have higher accuracy between iterations, which effectively mean that it was easier for us to focus on individual areas and know which areas needed attention. 
\\\\
Using standup meetings and pair programming, we achieved a higher level of knowledge sharing, and at the same time increased the quality of the software produced\todo{Vi ved sådan set ikke noget om det her endnu, så omformuler det hvis det ikke er sandt i fremtiden}. 
\\\\
Our experience shows that a user story and an acceptance test coexist in a mutual relationship. A user story draft is usually formulated first and a draft for an acceptance is then designed. The user story and acceptance test drafts are then revised back and forth until everyone claims to have understood both and have agreed on their semantics. User stories and their corresponding acceptance tests can be seen in \appref{app:user_stories_and_acceptance_test}.
\\\\
Nearing the end of the project period (approximately the last two-three iterations) the time schedule was becoming increasingly tighter, and we therefore changed from estimating all created tasks to only estimating tasks until we had enough work hours to fulfil the iteration work schedule. We felt this was necessary because there is a significant overhead in waiting for everybody to agree on how long a task is going to take. By making this change, we wanted the developers to feel that they were not wasting time \todo{do we need other reasons?}, and we therefore embraced this shift in development methodology.

\input{content/reflection/development_environment}