%!TEX root = ../../super_main.tex

\section{RESTful Maturity}
\label{sec:restful_maturity}

The Application Programming Interface (API) that we have implemented is a good beginning of a RESTful API. However, there are certain aspects that are missing in the resource representations that we send to the clients. If our API should be truly RESTful we should be following the principle of Hypermedia As The Engine Of Application State (HATEOAS), which specifies, that any resource should in itself present hyperlinks to every modification or other interaction with the object that could be taken. This means that when sending the list of campaigns to the client we should not only provide the id, the author, and the title of the different campaigns. It should also provide the link used to fetch all the information about the campaign; the link used for joining the campaign; and the link for uploading snapshots to the specific campaign. There exists a model for evaluating ``how RESTful'' an API is, called Richardson's Maturity Model \parencite{richardsons_model}, which rates RESTful API's on a scale from zero to three. The first level, 0, is not RESTful at all; the second, 1, is when one is starting to use the correct URI's; the third, 2, when you utilize the correct HTTP request methods in the API; and the lasts level, 3, is when you utilize HATEOAS and thereby is truly RESTFul. We believe that we would be placed on level 2, following all principles but the HATEOAS principle. However, the creator of the REST principles, Roy T. Fielding, writes in a blog post that he does not see the an API as RESTful unless it is hypertext driven (following HATEOAS)\parencite{http_manden_blog}, meaning that we, according to him, not are RESTful at all. 