%!TEX root = ../../super_main.tex

\section{Problem Definition} 
\label{sec:problem_definition}
% Opsumer analyse
% Legal stuff, Encryption stuff, ethics stuff
There is, as described in \secref{sub:legislation}, different types of data with different privacy requirements. Some of these requirements apply to this project and the data we intend to collect. We must therefore take measures to accommodate these requirements. 
\\\\
% Campaign definition(s)
We borrow the terminology from AndWellness \parencite{hicks2010andwellness} and define a campaign to be all the configuration of triggers, sensor data collection, and label questionnaires necessary for a session of data collection from participants.    
\\\\
% Health care stuff requires real time - Impacts battery
Available sensor gathering applications and accompanying platforms generally have real time goals, health care systems often have intervention goals which requires data to be synchronized with a central node in near real time. 
\\\\
% Does not allow dynamic use of sensors from other mobile devices than smartphones
The existing solutions we have looked at does not incorporate more devices than smartphones which in general does not have all the health monitoring sensor of for instance a smart watch or a smart band, which opposed to a smartphones are worn close to the body. One could for instance imagine that data from these sensors to be interesting in various health related classification problems. 
\\\\
% Participatory sensing and training data
The context of monitored ubiquitous devices, i.e. gathered sensor data, does necessarily not provide much value without being coupled with a meaningful class label which could for instance be the mental state of a participant through participatory sensing. The sensor data values, by them self, can only be used to train a model which predicts the behavior related to a subset of the sensors without the extra labels from participants. \todo{Måske en mere vag formulering eller kilde her?}

% Hovedspørgsmål 
\subsection{Problem Statement}
\label{sub:problem_statement}

%Current health s

The following problem statement and supporting subquestions are based on the prior analysis.
\\\\
\textbf{What characterizes a participatory sensing system which collects machine intelligence training data from distributed ubiquitous devices and how could such a system be realized?}

% Underspørsmål
\begin{itemize}
    \item How can we facilitate ad-hoc sensor data collection of different ubiquitous devices, which might and might not be present at a given time?
    \item How can we acquire class labels, from participants, for the sensor data context gathered from ubiquitous devices?  
    \item How can we allow customers to define a campaign for their participants?
    \item How can we minimize battery consumption from data gathering on mobile devices by exploiting that we little real time requirements?
    \item How can we maintain required privacy legislation and protect participants' sensitive personal data? 
\end{itemize}

